The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-11-21 paper/ms.tex
new abundances from madeline and keith
keith comment implemented, removed

{\bf Ben the tables should be remade to do Mg, Ti, Si, Ca, Al, V, Fe, Ni in on Table called differential abundances and second table of Sr, Y, Zr, Ba, La, Nd, Eu which is for the non-differential neutron capture} The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most  Arcturus differential abundances are not available, these are provided as supplementary online-only material. 
\input{stellar_props.tex}

\input{abundances_1.tex}
\input{abundances_2.tex}
\input{abundances_3.tex}

>>>>

\input{stellar_props.tex}

\input{abundances_1.tex}
\input{abundances_2.tex}
